---
title: "Fragility curve fitting tool"
author: "George Williams"
date: "21/03/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

The purpose of this document is to provide a flexible tool, to aid someone with little to no prior experience in coding in fitting fragility curves (quantitative vulnerability models) using their own data and to perform simple but often overlooked cross-validation and uncertainty calculations on their curves. 

The advantage of using this tool is that the user should be able to quickly produce easily editable plots of their curves, know the parameters for their curves (e.g. mean and dispersion/standard deviation) and should more damage data become availbale, users can quickly update curves.

## Outline

This tool implements two similar and commonly used fragility curve fitting approaches. One makes use of generalised linear models and the other, cumulative link models. The advantages and disadvantages of these approaches (along with several other alternatives) are described in Lallemant et al. (2015). For a more general background on fragility curve fitting please read the associated document 

## Input

The tool requires users to input damage data using a .csv file formatted with two columns and as many rows as there are observations of damage. One colunm must contain hazard intensity measurements whilst the other contains the damage states that resulted from each hazard intensity.  


```{r cars}
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
